Figure 3c

### 2017-12-04 inst/stable_line_growth_starvation/stable_line_growth_starvation.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
added a silent p-value calculation in growth analysis

>>>>

#unreported p-values per time point
p <- data %>% 
  filter(Time != 0) %>% 
  unite(tmp, `Biological Replicate`, `Cell line`) %>% 
  spread(tmp, techMean) %>% 
  group_by(Treatment, Time) %>% 
  summarize(
	  p = t.test(
	    c(`1_PC3 miR34a asRNA`, `2_PC3 miR34a asRNA`, `3_PC3 miR34a asRNA`), 
	    c(`1_PC3 Mock`, `2_PC3 Mock`, `3_PC3 Mock`)
	  )$p.value,
	  meanAS = mean(c(`1_PC3 miR34a asRNA`, `2_PC3 miR34a asRNA`, `3_PC3 miR34a asRNA`)),
	  meanMock = mean(c(`1_PC3 Mock`, `2_PC3 Mock`, `3_PC3 Mock`))
  ) %>%
  mutate(fold = meanAS / meanMock)
```
